Fitting metabolic models to dissolved oxygen data: the Estuarine BAyesian Single-station Estimation method

### 2023-05-01 manu-draft.qmd
added synthetic and synthetic noise comparison plot

@@

>>>>

As a final evaluation of EBASE to return known metabolic parameters, a new time series was created that added estimated effects of instrument and tidal noise to the synthetic time series.  This assessment provided information on the influence of common noise signals in dissolved oxygen time series on the estimation process for EBASE.  An assumption of the analysis is that EBASE will return similar parameters for a noisy time series as for those in the time series used above that did not include noise.  The instrument and tidal noise time series were first estimated by using a weighted regression analysis [@Beck15] on an actual observed dissolved oxygen time series for Apalachicola Bay using data from 2021.

@@

![A subset of the synthetic time series and the synthetic time series with noise for evaluating the ability of EBASE to recover known metabolic parameters.  The original synthetic time series and the same time series with instrument and tidal noise is shown in (a) and the estimated instrument and tidal noise is shown in (b).](figs/synapanos.png){#fig-synapanos fig-align="center"}

![Comparisons of modelled dissolved oxygen and metabolic parameters from EBASE for a synthetic time series and a synthetic time series with instrument and tidal noise. Black lines show the 1:1 comparison and the red lines show the linear regression fit. See @fig-synapanos for an example of the dissolved oxygen for both input time series.](figs/synapanoscmp.png){#fig-synapanoscmp fig-align="center"}
